\documentclass[11pt]{ltxdoc}
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{natbib}
  \usepackage{microtype}
  \usepackage[scaled=0.90]{helvet}
  \usepackage[scaled=1.02]{inconsolata}
  \usepackage[sc]{mathpazo}
  \usepackage{rsfso}
  \usepackage{actuarialsymbol}[2017/04/10]
  \usepackage{longtable,booktabs}

  %% colors
  \usepackage{xcolor}
  \definecolor{url}{rgb}{0.6,0,0}      % dark red
  \definecolor{citation}{rgb}{0,0.5,0} % dark green

  %% single entry for symbol and shortcut lists
  %% http://tex.stackexchange.com/a/128441
  \usepackage{xparse}
  \ExplSyntaxOn
  \NewDocumentCommand{\showcase}{v} { \tl_rescan:nn { } { $#1$ } & \texttt{#1} }
  \NewDocumentCommand{\rshowcase}{v} { \texttt{#1} & \tl_rescan:nn { } { $#1$ } }
  \ExplSyntaxOff

  %% utility macro
  \newcommand{\pkg}[1]{\textsf{#1}}

  %% increase row height in tables
  \renewcommand{\arraystretch}{1.2}

  %% hyperlinks
  \usepackage{hyperref}
  \hypersetup{colorlinks, linktocpage,
    urlcolor=url, citecolor=citation,
    bookmarksopen, bookmarksnumbered, bookmarksdepth=subsection,
    pdftitle={actuarialsymbol User Guide},
    pdfauthor={David Beauchemin, Vincent Goulet}}

  \title{Comprehensive life contingencies symbol list%
    \thanks{This document is an excerpt from the documentation of the
      {\LaTeX} package \pkg{actuarialsymbol} \citep{actuarialsymbol}.}}
  \author{David Beauchemin \\
    \url{david.beauchemin.5@ulaval.ca}
    \and
    Vincent Goulet\thanks{%
      École d'actuariat, Université Laval} \\
    \url{vincent.goulet@act.ulaval.ca}}
  \date{}

\begin{document}

\maketitle

This document is inspired by \citet{Trivedi:lifecon:2004}. The title
is a nod to the immensely useful \emph{Comprehensive {\LaTeX} Symbol
  List} of \citet{comprehensive}.

The table below contains all the life contingencies symbols listed in
Appendix~3 of \citet{Bowers:2e:1997} along with the code to compose
them with package \pkg{actuarialsymbol} (and therefore
\pkg{actuarialangle}) loaded. Often times there are various ways to
obtain a symbol; we tried to always present the most compact and
legible option. Not all symbols require features of
\pkg{actuarialsymbol}.

Calligraphic letters are typeset using \cmd{\mathcal}. The specific
versions of $\mathcal{L}$ and $\mathcal{D}$ that appear in this
table require package \pkg{rsfso} \citep{rsfso}, which is \emph{not}
loaded by \pkg{actuarialsymbol}. Standard versions of the
calligraphic letters are $\text{\usefont{OMS}{zplm}{m}{n} L}$ and
$\text{\usefont{OMS}{zplm}{m}{n} D}$. See Table~299 of
\citet{comprehensive} for other options.

\input{symbols}

\begin{thebibliography}{5}
  \addcontentsline{toc}{section}{References}
\bibitem[Beauchemin and Goulet(2017)]{actuarialsymbol}
  D.~Beauchemin and V.~Goulet.
  \newblock \emph{Actuarial symbols of life contingencies and financial
    mathematics}, 2017.
  \newblock URL \url{http://www.ctan.org/pkg/actuarialsymbol/}.

\bibitem[Bowers et~al.(1997)Bowers, Gerber, Hickman, Jones, and
  Nesbitt]{Bowers:2e:1997}
  N.~L. Bowers, H.~U. Gerber, J.~C. Hickman, D.~A. Jones, and C.~J. Nesbitt.
  \newblock \emph{Actuarial Mathematics}.
  \newblock Society of Actuaries, Shaumburg, IL, second edition, 1997.
  \newblock ISBN 0-9389594-6-8.

\bibitem[Pakin(2015)]{comprehensive}
  S. Pakin.
  \newblock \emph{The Comprehensive {\LaTeX} Symbol List}, 2015.
  \newblock URL \url{http://www.ctan.org/pkg/comprehensive/}.

\bibitem[Sharpe(2015)]{rsfso}
  M. Sharpe.
  \newblock \emph{An acute script font based on {rsfs}}, 2015.
  \newblock URL \url{http://www.ctan.org/pkg/rsfso/}.

\bibitem[Trivedi(2004)]{Trivedi:lifecon:2004}
  E. Trivedi.
  \newblock \emph{Life Contingencies' Symbols}, 2004.
  \newblock \texttt{lifecon} 2.1 User Guide.
\end{thebibliography}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
